%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
% customizing link colors and formatting
%\hypersetup{colorlinks=true}
%\hypersetup{a4paper=true}
\usepackage{color}
\definecolor{iorange}{RGB}{243,110,36}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%PERSONAL DATA%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% personal data
\firstname{Imran}
\familyname{Ahmed}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{\hspace{-1in}S. No. 165/3/1/2, \\Gurudwara Colony,\\Lohegaon,}{Pune, 411047}    % optional, remove the line if not wanted
\mobile{mobile +91-9762742899}                    % optional, remove the line if not wanted
%\phone{}                      % optional, remove the line if not wanted
\email{iahmed213@gmail.com}                      % optional, remove the line if not wanted
%\homepage{reversehack.in}
\extrainfo{IRC Nick: rekenerd}
\extrainfo{GitHub: github.com/rekenerd \\Blog: rekenerd.github.com}                

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%EDUCATION%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\cventry{2012-Present}{Software Developer}{}{Hopsys}{India}{}\\
\cventry{2008-2012}{Completed engineering in Computer Science}{}{University of Pune}{India}{Studied at Jayawantrao Sawant College of Engineering. Secured higher second class.\\
Graduated in June, 2012.}  
\cventry{2007-2008}{HSC}{CBSE}{Pune}{IN}{Secured 79.6\%} % arguments 3 to 6 are optional
\cventry{2005-2006}{SSC}{CBSE}{Pune}{IN}{Sesured 81.6\%}  % arguments 3 to 6 are optional

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%TECHNICAL SKILLS%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvcomputer{}{} {}{}

\vspace{.4in}\section{Technical Skills} 
\cvcomputer{\textbf{Platforms}}{GNU/Linux(Debian,Fedora),\\Android, Microsoft\textsuperscript{\textregistered} Windows\textsuperscript{\textregistered}.}{\textbf{Programming Languages Used}}{C, C++, Python: Intermediate. \\ Java, Ruby, Scala: Beginner. } {}{}
\cvcomputer{\textbf{Frameworks}}{Rails, Django.}{\textbf{Databases}}{MySQL, Oracle, SQLite.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%EXPERIENCE%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
%AndroSync
\cventry
{2011-Present}
{AndroSync}
{Final year engineering project}
{}
{}
{Currently working on AndroSync; an offline android synchronization manager specifically being built for linux platform but is cross-platform 
compatible. AndroSync can be used to avoid sending user data to cloud during back up of contacts, messages, etc and ensure users privacy. 
Consists of client and server module. Client is an android application and server is a desktop application written using Qt, C++ and SQLite.}


%PyGame
\cventry
{May, 2011}
{PyGame}
{Third year engineering mini-project}
{}
{}
{This project was an attempt to learn python and simple animation using python pygame libraries. Built simple applications like paint and toy 
animations. A tron like game was built as part of this project. }

%eventIT
\cventry
{May, 2011}
{EventIt}
{Third year engineering mini-project}
{}
{}
{Created a website for event organisation. Useful for tasks like ticketing, updates, FAQs, etc. using PHP, CSS, MySQL. }

%LIC
\cventry
{September, 2010}
{Insurance record manager}
{Third year engineering mini-project}
{}
{}
{As part of the curriculum, created a mini-project for handling records of a life insurance firm using VB, Oracle 10g. }


\section{Seminars Conducted}
%\subsection{Vocational}
%\cventry{2010--Present}{Network and System Administrator}{\textcolor{iorange}{iIntelliSys}}{Pune}{IN}{}                % arguments 3 to 6 are optional

%\subsection{Open Source Contributions}


%Diaspune

\cventry
{February 2011}
{Python with Pygame for Beginners}
{}
{}
{}
{Basic introduction to programming in Python. Usage of python for simplifying programming tasks and using graphics libraries for animation.}

\cventry
{May 2011}
{Secure Sockets Layer}
{JSCOE}
{Speaker}
{}
{Presented this seminar as part of curriculum based on \hyperlink{http://ieeexplore.ieee.org/search/freesrchabstract.jsp?tp=&arnumber=1621007}{IEEE 
paper}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%Co-Curricular%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Co-Curricular}
\subsection{Talks and Workshops attended}
\cventry{}{* Introduction to Ruby and Ruby on Rails}{}{}{}{}
\cventry{}{* RubyConf 2012}{}{}{}{}
\cventry{}{* Agile programming practices}{}{}{}{}
%\cventry{}{* FudCon 2011}{}{}{}{}
%\cventry{}{* Fedora Activity Day, 2011}{}{}{}{}
\cventry{}{* Version controlling using Git}{}{}{}{}
%\cventry{}{* Fedora packaging}{}{}{}{}
\cventry{}{* PyCon 2011}{}{}{}{}
\cventry{}{* MiniDebianConference 2010, 2011}{}{}{}{}
\cventry{}{* GNUnify2011}{}{}{}{}
\cventry{}{* Programming in Python}{}{}{}{}
\cventry{}{* Android application development basics}{}{}{}{}
%\cventry{}{* Joomla Day 2011}{}{}{}{}	
\cventry{}{* Microsoft .Net framework}{}{}{}{}
\cventry{}{* Cloud Computing (Cloud Camp)}{}{}{}{}	
%\newpage
\subsection{Other}
\cventry{}{* Volunteered for RubyConf 2012}{}{}{}{}	
\cventry{}{* Active member of the Diaspora Pune group}{}{}{}{}	
\cventry{}{* Member of Pune Linux User’s Group (PLUG) and VIT Active Linux Users group (VALU). }{}{}{}{}	
\cventry{}{* Participated at various inter-college level technical events}{}{}{}{}
%\cventry{}{* Participated in College Festivals}{}{}{}{}
\cventry{}{* Member of college basketball team}{}{}{}{}		

%\cvlistitem{ Item 1}
%\cvlistitem{ Item 2
% \\http://example.com
%  \\http://example2.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%INTERESTS & HOBBIES%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Interests and Hobbies}
\cvline{Privacy and Security}{\small I like to spread awareness about Key signing, online privacy. I like to educate people on how to use internet 
safely. }
\cvline{Blogging}{\small I like to blog about my thoughts, technology and any enlightening events of my life.}
%\cvline{Reading}{\small Reading technical blogs, journals, technical books and fictional and non-fiction novels.} 
\cvline{IRCing}{\small I like to use the IRC for learning and helping out people.}
%\cvline{E-Gadgets}{\small I like to explore new electronic gadgets.}
%\cvline{Travelling}{\small I love traveling and trekking on weekends.}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\end{document}
